Boundary Labeling for annotated documents

### 2017-09-28 LaTeX/Paper.tex
Paper: Finished Re-work of the Graph-related terminology. Probram: No changes.

\settitle{TestTitle}{TestTitel}
\setsubtitle{TestSubtitle}{TestSubtitel}

@@

For example, the paper about the Luatodonotes-Package\cite{Kindermann2014} illustrates some of the different styles of drawing these connecting paths, and came to the conclusion that paths without bends are easier to follow. %Bild einfügen?
However, most solutions proposed in that paper don't care whether a path overlapped with text or not, which results in a decrease in readability.

@@

A \emph{Graph} $G=\langle V, E \rangle$ is a tuple of \emph{Vertices} (V) and \emph{Edges} (E).Vertices are... % Each edge $e_i~\in~E \, (i~\in~\mathbb{N})$ is

\begin{itemize}
 \item \textbf{Graph:} A Tuple of Vertices and Edges (see below), often used to represent routing problems. Can be further classified depending on its properties.
 \item \textbf{Edge:} A connection between two vertices, usually represented as a line. Can be directional, limiting its usage, or have a cost (``Weight'') associated with its use.
 \item \textbf{Vertex:} A featureless object that can be connected to any number other vertices via edges. Usually depicted as a point or small shape. Also referred to as \textbf{``Node''}.%Remove second sentence and re-define node?
 \item \textbf{Path:} An ordered series of either edges that share one vertex each with the edges listed before and after them, or an ordered series of vertices that have an edge connecting each vertex to the subsequent one. Also known as \textbf{``Graph Walk''}.

>>>>

\settitle{Boundary Labeling for annotated documents}{Boundary Labeling in annotierten Dokumenten}
\setsubtitle{TestSubtitle}{TestSubtitel}

@@

For example, the paper about the Luatodonotes-Package\cite{Kindermann2014} illustrates some of the different styles of drawing these connecting paths, and came to the conclusion that paths without bends are easier to follow. %Bild einfügen?
However, most solutions proposed in that paper do not consider whether a path overlapped with text or not, which results in a decrease in readability.

@@

A \emph{Graph} $G=\langle V, E \rangle$ is a tuple of \emph{Vertices} $(V=\{v_1, v_2, ..., v_n\})$ and \emph{Edges} $(E=\{e_1, e_2, ..., e_m\})$. A Vertex $v_i (i~\in~\mathbb{N})$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e_i \, (i~\in~\mathbb{N})$ is a relation between two vertices (Therefore: $E:V\rightarrow  V\times V$). The vertices forming the edge are considered \em{adjacent} to each other. Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
 A \em{Path} $(P=v_1, ..., v_h)$ is an ordered series of vertices, where each vertex must have an edge connecting it to the subesquent one.

\begin{itemize}
% \item \textbf{Graph:} A Tuple of Vertices and Edges (see below), often used to represent routing problems. Can be further classified depending on its properties.
% \item \textbf{Edge:} A connection between two vertices, usually represented as a line. Can be directional, limiting its usage, or have a cost (``Weight'') associated with its use.
% \item \textbf{Vertex:} A featureless object that can be connected to any number other vertices via edges. Usually depicted as a point or small shape.
% \item \textbf{Path:} An ordered series of either edges that share one vertex each with the edges listed before and after them, or an ordered series of vertices that have an edge connecting each vertex to the subsequent one. Also known as \textbf{``Graph Walk''}.
